RDF Validation of Metadata \\ on Highly-Complex Person-Level Data

### 2015-02-21 paper/paper7/paper7-appendix.tex
technology-driven validation

\begin{itemize}
	\item \textbf{{\em DISCO-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{Disco} object and data property.
  Only {\em disco:Question}s, e.g., can have {\em disco:responseDomain} relationships (\ms{$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question}).
	Severity level: ERROR
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{Data Cube} object and data property.
  Only {\em qb:Observation}s, e.g., can have {\em qb:dataSet} relationships (\ms{$\exists$ dataSet.$\top$ $\sqsubseteq$ Observation}).
	Severity level: ERROR
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{DCAT} object and data property.
  Only {\em dcat:Catalog}s, e.g., can have {\em dcat:dataset} relationships (\ms{$\exists$ dataset.$\top$ $\sqsubseteq$ Catalog}).
	Severity level: ERROR
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{PHDD} object and data property.
  Only {\em phdd:Table}s, e.g., can have {\em phdd:isStructuredBy} relationships (\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}).
	Severity level: ERROR
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{Disco} object and data property.
  {\em disco:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
	Severity level: ERROR
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{Data Cube} object and data property.
  {\em qb:order} relationships, e.g., can only point to literals of the datatype {\em xsd:string} (\ms{$\top$ $\sqsubseteq$ $\forall$ order.string}).
	Severity level: ERROR
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{DCAT} object and data property.
  {\em dcat:bytes} relationships, e.g., can only point to literals of the datatype {\em xsd:integer} (\ms{$\top$ $\sqsubseteq$ $\forall$ bytes.integer}).
	Severity level: ERROR
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{PHDD} object and data property.
  {\em phdd:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
	Severity level: ERROR
\end{itemize}

@@

Concept inclusions allow us to state that all mothers are female and that
all mothers are parents, but what we really mean is that mothers are exactly the female
parents. DLs support such statements by allowing us to form complex concepts such as
the \emph{intersection}\footnote{\ms{R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS}, \ms{R-16-CONJUNCTION-OF-DATA-RANGES}} (also called \emph{conjunction})
which denotes the set of individuals that are both female and parents. A complex concept
can be used in axioms in exactly the same way as an atomic concept, e.g., in the
equivalence Mother $\equiv$ Female $\sqcap$ Parent .

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-01:}}
	Dimensions have range (\emph{IC-4} \cite{CyganiakReynolds2014}) - 
	Every dimension declared in a \emph{qb:DataStructureDefinition} must have a declared \emph{rdfs:range}. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-02:}}
	Concept dimensions have code lists (\emph{IC-5} \cite{CyganiakReynolds2014}) - 
	Every dimension with range \emph{skos:Concept} must have a \emph{qb:codeList}. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-03:}} 
	Slice dimensions complete (\emph{IC-10} \cite{CyganiakReynolds2014}) - 
	Every \emph{qb:Slice} must have a value for every dimension declared in its \emph{qb:sliceStructure}. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-04:}}
	All dimensions required (\emph{IC-11} \cite{CyganiakReynolds2014}) - 
	Every \emph{qb:Observation} has a value for each dimension declared in its associated \emph{qb:DataStructureDefinition}. 
  \item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-05:}}
	DSD includes measure (\emph{IC-3} \cite{CyganiakReynolds2014}) -  
	Every \emph{qb:DataStructureDefinition} must include (\emph{qb:component}, \emph{qb:componentProperty}) at least one declared measure. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-06:}}
	Slice Keys must be declared (\emph{IC-7} \cite{CyganiakReynolds2014}) -
	Every \emph{qb:SliceKey} must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition}. 
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-UNIVERSAL-QUANTIFICATIONS-01:}}
Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s (\ms{LogicalDataSet $\sqsubseteq$ $\forall$ aggregation.DataSet}).
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
A {\em disco:Questionnaire} has at least one {\em disco:question} relationship to {\em disco:Question} (\ms{Questionnaire $\sqsubseteq$ $\geq$1 question.Question}).
\end{itemize}

@@

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
	Unique slice structure (\emph{IC-9} \cite{CyganiakReynolds2014}) -  
	Each \emph{qb:Slice} must have exactly one associated \emph{qb:sliceStructure}. 
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe} (\ms{Question $\sqsubseteq$ $\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe}).
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
	Unique data set (\emph{IC-1} \cite{CyganiakReynolds2014}) -  
	Every \emph{qb:Observation} has (\emph{qb:dataSet}) exactly one associated \emph{qb:DataSet}. 
	\item \textbf{{\em DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02:}}
	Unique DSD (\emph{IC-2} \cite{CyganiakReynolds2014}) -  
	Every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition}. 
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTY-GROUPS-01:}}
Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as DDI concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as DDI codes and categories), but not both.

>>>>

\begin{itemize}
	\item \textbf{{\em DISCO-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{Disco} object and data property.
  Only {\em disco:Question}s, e.g., can have {\em disco:responseDomain} relationships (\ms{$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{Data Cube} object and data property.
  Only {\em qb:Observation}s, e.g., can have {\em qb:dataSet} relationships (\ms{$\exists$ dataSet.$\top$ $\sqsubseteq$ Observation}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{DCAT} object and data property.
  Only {\em dcat:Catalog}s, e.g., can have {\em dcat:dataset} relationships (\ms{$\exists$ dataset.$\top$ $\sqsubseteq$ Catalog}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{PHDD} object and data property.
  Only {\em phdd:Table}s, e.g., can have {\em phdd:isStructuredBy} relationships (\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em SKOS-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{SKOS} object and data property.
	Only {\em skos:ConceptSchemes}, e.g., can have {\em skos:hasTopConcept} relationships (\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em XKOS-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{XKOS} object and data property.
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{Disco} object and data property.
  {\em disco:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{Data Cube} object and data property.
  {\em qb:order} relationships, e.g., can only point to literals of the datatype {\em xsd:string} (\ms{$\top$ $\sqsubseteq$ $\forall$ order.string}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{DCAT} object and data property.
  {\em dcat:bytes} relationships, e.g., can only point to literals of the datatype {\em xsd:integer} (\ms{$\top$ $\sqsubseteq$ $\forall$ bytes.integer}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{PHDD} object and data property.
  {\em phdd:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em SKOS-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{SKOS} object and data property.
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em XKOS-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{XKOS} object and data property.
  {\em xkos:belongsTo} relationships, e.g., can only point to instances of the class {\em skos:Concept} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

@@

Concept inclusions allow us to state that all mothers are female and that
all mothers are parents, but what we really mean is that mothers are exactly the female
parents. DLs support such statements by allowing us to form complex concepts such as
the \emph{intersection}\footnote{\emph{R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS}, \emph{R-16-CONJUNCTION-OF-DATA-RANGES}} (also called \emph{conjunction})
which denotes the set of individuals that are both female and parents. A complex concept
can be used in axioms in exactly the same way as an atomic concept, e.g., in the
equivalence Mother $\equiv$ Female $\sqcap$ Parent .

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-01:}}
	Dimensions have range (\emph{IC-4} \cite{CyganiakReynolds2014}) - 
	Every dimension declared in a \emph{qb:DataStructureDefinition} must have a declared \emph{rdfs:range}. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-02:}}
	Concept dimensions have code lists (\emph{IC-5} \cite{CyganiakReynolds2014}) - 
	Every dimension with range \emph{skos:Concept} must have a \emph{qb:codeList}. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-03:}} 
	Slice dimensions complete (\emph{IC-10} \cite{CyganiakReynolds2014}) - 
	Every \emph{qb:Slice} must have a value for every dimension declared in its \emph{qb:sliceStructure}. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-04:}}
	All dimensions required (\emph{IC-11} \cite{CyganiakReynolds2014}) - 
	Every \emph{qb:Observation} has a value for each dimension declared in its associated \emph{qb:DataStructureDefinition}. 
  \item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-05:}}
	DSD includes measure (\emph{IC-3} \cite{CyganiakReynolds2014}) -  
	Every \emph{qb:DataStructureDefinition} must include (\emph{qb:component}, \emph{qb:componentProperty}) at least one declared measure. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-06:}}
	Slice Keys must be declared (\emph{IC-7} \cite{CyganiakReynolds2014}) -
	Every \emph{qb:SliceKey} must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}). 
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-UNIVERSAL-QUANTIFICATIONS-01:}}
	\emph{Universal quantifications} are defined for each \emph{Data Cube} object and data property.
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-UNIVERSAL-QUANTIFICATIONS-01:}}
	\emph{Universal quantifications} are defined for each \emph{DCAT} object and data property.
	Only {\em dcat:Catalogs} can have {\em dcat:dataset} relationships to {\em dcat:Datasets} (\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DISCO-C-UNIVERSAL-QUANTIFICATIONS-01:}}
	\emph{Universal quantifications} are defined for each \emph{Disco} object and data property.
  Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s (\ms{LogicalDataSet $\sqsubseteq$ $\forall$ aggregation.DataSet}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-UNIVERSAL-QUANTIFICATIONS-01:}}
	\emph{Universal quantifications} are defined for each \emph{PHDD} object and data property.
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em SKOS-C-UNIVERSAL-QUANTIFICATIONS-01:}}
	\emph{Universal quantifications} are defined for each \emph{SKOS} object and data property.
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em XKOS-C-UNIVERSAL-QUANTIFICATIONS-01:}}
	\emph{Universal quantifications} are defined for each \emph{XKOS} object and data property.
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{Data Cube} object and data property.
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{DCAT} object and data property.
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{Disco} object and data property.
  A {\em disco:Questionnaire}, e.g., has at least one {\em disco:question} relationship to {\em disco:Questions} (\ms{Questionnaire $\sqsubseteq$ $\geq$1 question.Question}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{PHDD} object and data property.
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
	A {\em disco:Variable} has at most one {\em disco:concept} relationship to a theoretical concept ({\em skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
	Unique slice structure (\emph{IC-9} \cite{CyganiakReynolds2014}) -  
	Each \emph{qb:Slice} must have exactly one associated \emph{qb:sliceStructure}. 
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe} (\ms{Question $\sqsubseteq$ $\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe}).
  \begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
	Unique data set (\emph{IC-1} \cite{CyganiakReynolds2014}) -  
	Every \emph{qb:Observation} has (\emph{qb:dataSet}) exactly one associated \emph{qb:DataSet} (\ms{Observation $\sqsubseteq$ $\geq$1 dataSet.DataSet $\sqcap$ $\leq$1 dataSet.DataSet}). 
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02:}}
	Unique DSD (\emph{IC-2} \cite{CyganiakReynolds2014}) -  
	Every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}). 
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTY-GROUPS-01:}}
Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both.

### 2015-02-21 paper/paper7/paper7.tex
technology-driven validation

Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
This technical report also contains mappings to description logics to logically underpin each requirement and to determine which description logics constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
Bosch et al. recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/XXXXX}} (serving as appendix of this paper) in which we describe RDF constraints to validate metadata on person-level and aggregated data.
We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types
\cite{BoschZapilkoWackerowEckert2015}.

We distinguish two validation types:
\emph{Content-Driven Validation} contains the set of constraints ensuring that the data is consistent with the intended semantics of data models,
i.e. the integrity of the data according to data models.
\emph{Technology-Driven Validation} includes the set of constraints which can be generated automatically out of defined data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
We determined the default \emph{severity level}\footnote{Corresponds to \emph{R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS}} for each constraint indicating how serious the violation of the constraint is.
The continuum of \emph{severity levels} ranges from informational via warning and error to fatal error. 
Although we provide default \emph{severity levels} for each constraint, users should be able to specify \emph{severity levels} of constraints they need to validate within the context of their individual use cases.
Therefore, use case specific \emph{severity levels} can be defined for constraints.

@@

\textbf{Surveys.}
Each survey must have an abstract\footnote{\emph{ DISCO-C-DATA-PROPERTY-FACETS-01}}. 
If the abstract of the survey is missing, a title of the survey has to be stated\footnote{\emph{DISCO-C-CONDITIONAL-PROPERTIES-02}}.

@@

\textbf{Theoretical Concepts.}
Variables must have at least one relation to a theoretical concept.
The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The severity level of this constraint is a warning and not an error, as research can be continued without an associated theoretical concept.

\textbf{Variable Comparisons\footnote{Constraint types: \emph{DISCO-C-COMPARISON-VARIABLES-XX}}.}
One very common research question is to compare variables of multiple surveys or countries.
To compare variables, 
(1) variables and (2) variable definitions must be present,
(3) code lists must be structured properly,
(4) for each code an associated category (human-readable label) must be specified, and
(5) code lists must either be identical or at least similar.
If a researcher wants to get a first overview over comparable variables (use case 1), 
the first three constraints may be sufficient for this purpose.
Thus, the \emph{severity level} of the first three constraints is stronger than the \emph{severity level} of the next constraints.
If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining constraints is also more serious.

@@

>>>>

Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
The knowledge representation formalism {\em Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
Bosch et al. recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/XXXXX}} (serving as appendix of this paper) in which we describe RDF constraints to validate metadata on person-level and aggregated data.
We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types
\cite{BoschZapilkoWackerowEckert2015}.

We distinguish two validation types:
\emph{Content-Driven Validation} contains the set of constraints ensuring that the data is consistent with the intended semantics of data models,
i.e. the integrity of the data according to data models.
\emph{Technology-Driven Validation} includes the set of constraints which can be generated automatically out of defined data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
We determined the default \emph{severity level}\footnote{Corresponds to \emph{R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS}} for each constraint indicating how serious the violation of the constraint is.
The continuum of severity levels ranges from informational via warning and error to fatal error. 
Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate within the context of their individual use cases.
Therefore, use case specific severity levels can be defined for constraints.

@@

\textbf{Surveys.}
Each survey must have an abstract\footnote{\emph{DISCO-C-DATA-PROPERTY-FACETS-01}}. 
If the abstract of the survey is missing, a title of the survey has to be stated\footnote{\emph{DISCO-C-CONDITIONAL-PROPERTIES-02}}.

@@

\textbf{Theoretical Concepts.}
Variables must have at least one relationship to a theoretical concept\footnote{{\em DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01}}.
%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The variable \emph{Education at pre-school}, e.g., is associated with the theoretical concept \emph{education}. 
The severity level of this constraint is \emph{warning} and not \emph{error}, as research can be continued without an associated theoretical concept.

One very common research question is to \emph{compare variables}\footnote{Constraint types: \emph{DISCO-C-COMPARISON-VARIABLES-XX}} of multiple surveys or countries.
To compare variables, 
(1) variables and (2) variable definitions must be present,
(3) code lists must be structured properly,
(4) for each code an associated category (human-readable label) must be specified, and
(5) code lists must either be identical or at least similar.
If a researcher wants to get a first overview over comparable variables (use case 1), 
the first three constraints may be sufficient for this purpose.
Thus, the severity level of the first three constraints is stronger than the severity level of the next constraints.
If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining constraints is also more serious.

Constraints of the constraint type \emph{Context-Specific Exclusive OR of Property Groups}
restrict individuals of given classes to have only one of multiple property groups\footnote{{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}}.
Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both\footnote{\emph{DISCO-C-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTY-GROUPS-01:}}.

\begin{DL}
Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C) \\ 
D $\equiv$ A $\sqcap$ B \\
A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
\end{DL}

@@

Constraints of some constraint types are directly and automatically derived from conceptual models of multiple vocabularies.
This way, \emph{property domains and ranges, universal and existential quantifications, minimum, maximum, and exact cardinality restrictions} are defined for each object and data property of vocabularies against which one wish to validate.
As these constraints directly depend on the intended semantics of data models, associated severity levels are very strong.

{\em Property Domains}\footnote{{\em R-25-OBJECT-PROPERTY-DOMAIN}, {\em R-26-DATA-PROPERTY-DOMAIN}} and {\em Ranges}\footnote{{\em R-28-OBJECT-PROPERTY-RANGE}, {\em R-35-DATA-PROPERTY-RANGE}}restrict domains and ranges of properties.
Only {\em skos:ConceptSchemes}, e.g., can have {\em skos:hasTopConcept} relationships (\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme}) and
{\em xkos:belongsTo} relationships can only point to instances of the class {\em skos:Concept} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
A \emph{universal quantification}\footnote{{\em R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}} contains all those individuals that are connected by a property only to individuals/literals that are instances of particular classes  or data ranges.
Only {\em dcat:Catalogs}, e.g., can have {\em dcat:dataset} relationships to {\em dcat:Datasets} (\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}).
An \emph{existential quantification}\footnote{{\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}} contains all those individuals that are connected by a property to individuals/literals that are instances of given classes or data ranges.
Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
\emph{Minimum/maximum/exact qualified cardinality restrictions}\footnote{\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES, \\ R-76-MAXIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES, \\ R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES}} contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals that are instances of particular classes or data ranges.
\emph{Minimum qualified cardinality restrictions} are defined for each property of multiple vocabularies like \emph{Disco}.
A \emph{disco:Questionnaire}, e.g., has at least one {\em disco:question} relationship to {\em disco:Questions} (\ms{Questionnaire $\sqsubseteq$ $\geq$1 question.Question}),
a {\em disco:Variable} has at most one {\em disco:concept} relationship to a theoretical concept ({\em skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
%\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.

-----

reasoning constraints / sub-classes / sub-properties
